\documentclass{article}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{amsmath}

\title{FYS9411 -- Project 1}
\author{Ingvild Bergsbak}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}

\section{Background}
\subsection{Particle in harmonic trap}
	\subsubsection{One particle}
	\subsubsection{Many particles}
	\subsubsection{Elliptic trap}
\subsection{Variational Monte Carlo}
\subsection{Importance sampling}
\subsection{Steepest decent algorithm}

\section{Analytic expressions}

\subsection{Local energy, no interaction}
1, 2 and 3 dimensions for 1 and $N$ particles.

\subsubsection{One dimension}

The local energy, $E_L$, and the Hamiltonian, $H$, is given by the general expression 

$$E_L(\mathbf{r})=\frac{1}{\Psi_T(\mathbf{r})}H\Psi_T(\mathbf{r}) ,\quad H=\sum_{i}^{N}\frac{-\hbar^2}{2m}\nabla_i^2+\tfrac{1}{2}m\omega_{ho}^2r_i^2$$

For one particle $\mathbf{r}$ becomes
$$\mathbf{r}=x$$
where $x$ is the coordinate of the particle. The wave function and Hamiltonian becomes 
$$\Psi_T(\mathbf{r})=\Psi_T(x)=e^{-\alpha x^2}$$
$$H=\frac{-\hbar^2}{2m}\frac{d^2}{dx^2}+\tfrac{1}{2}m\omega_{ho}^2x^2$$
which gives the local energy
$$E_L(x)=\frac{1}{\Psi_T(x)}H\Psi_T(x)=\frac{1}{e^{-\alpha x^2}}\Big(\frac{-\hbar^2}{2m}\frac{d^2}{dx^2}+\tfrac{1}{2}m\omega_{ho}^2x^2\Big)e^{-\alpha x^2}=\frac{\hbar^2}{m} \alpha x+\tfrac{1}{2}m\omega_{ho}^2x^2$$

For $N$ particles $\mathbf{r}$ becomes
$$\mathbf{r}=(x_1, x_2, ..., x_N)$$

\subsection{Drift force}
1, 2 and 3 dimensions.

\subsection{Local energy, with interaction}
3 dimensions for $N$ particles.

\section{Calculating the ground state energy}

\subsection{Variational Monte Carlo}
Variational Monte Carlo: starts with trial wave function, varies the parameters of the wave function to find an energy minimum

1, 2 and 3 dimensions, $N$=1, 10, 100, 500 (12 plot)

\subsection{Importance sampling}
1, 2 and 3 dimensions. Study the result as a function of the time step, $\delta t$
Discuss differences between brute force (Metropolis) and importance sampling. 

\subsection{Steepest decent algorithm}
Finding optimal $\alpha$ before the Monte Carlo cycles. Compare the computation time.

\subsection{Error analysis}

\subsection{Parallelizing the code}
Compare computation time.

\subsection{Repulsive interaction}
Elliptic trap, introducing length and energy units. Show new expression for the Hamiltonian. What is the expression for $\gamma$? Vary $\alpha$ for $N$=10, 50, 100 and compare to ideal case. Compare results to Refs.

\subsection{Onebody densities}
Compute the onebody density with and without the Jastrow factor, and discuss the importance of the correlations induced by the Jastrow factor.

\section{Conclusion}
Summarize results.

\end{document}